---
title: "Demographic, Social, Economic, and Housing Characteristics for Kingsport, TN"
author: "Paul Collins"
date: '`r format(Sys.Date(), "%m/%d/%Y")`'
output: 
  prettydoc::html_pretty:
    theme: cayman
bibliography: bibli.bibtex 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

This report highlights and describes selected socal , social, economic, and housing characteristics of Sullivan County, Tennessee, with special focus on the Kingsport City, IF I CAN GET THE CENCUS TRACTS THAT IT ENCOMPASSES, using data from the U.S. Census Bureau's American Community Survey data collected between 2013 and 2018. The data included is given in both the county wide levels for Sullivan and Hawkins Counties, as well as individual census tracts for detailed mapping and location data. In this report, special focus is given on 



```{r load packages, include=FALSE}
packages <- c("acs", "tidyverse", "tidycensus", "tigris", "leaflet", "mapview", "tmap", "DT", "sf", "gganimate", "report")

lapply(packages, library, character.only = TRUE)


```

```{r load data, echo = FALSE, include = FALSE}
dp_table_variables <- load_variables(2018, "acs5/profile", cache = TRUE)


new_names <- c("variable", "label", "concept")

names(dp_table_variables) <- new_names

Sullivan_dp02_2018 <- get_acs(geography = "tract", county = "Sullivan", state = "TN", table = "DP02", year = 2018, geometry = TRUE)

Sullivan_dp03_2018 <- get_acs(geography = "tract", county = "Sullivan", state = "TN", table = "DP03", year = 2018, geometry = TRUE)

Sullivan_dp04_2018 <- get_acs(geography = "tract", county = "Sullivan", state = "TN", table = "DP04", year = 2018, geometry = TRUE)

Sullivan_dp05_2018 <- get_acs(geography = "tract", county = "Sullivan", state = "TN", table = "DP05", year = 2018, geometry = TRUE)

Hawkins_dp02_2018 <- get_acs(geography = "tract", county = "Hawkins", state = "TN", table = "DP02", year = 2018, geometry = TRUE)

Hawkins_dp03_2018 <- get_acs(geography = "tract", county = "Hawkins", state = "TN", table = "DP03", year = 2018, geometry = TRUE)

Hawkins_dp04_2018 <- get_acs(geography = "tract", county = "Hawkins", state = "TN", table = "DP04", year = 2018, geometry = TRUE)

Hawkins_dp05_2018 <- get_acs(geography = "tract", county = "Hawkins", state = "TN", table = "DP05", year = 2018, geometry = TRUE)

Sullivan_dp02_18 <- inner_join(Sullivan_dp02_2018, dp_table_variables, by = "variable")

Sullivan_dp03_18 <- inner_join(Sullivan_dp03_2018, dp_table_variables, by = "variable")

Sullivan_dp04_18 <- inner_join(Sullivan_dp04_2018, dp_table_variables, by = "variable")

Sullivan_dp05_18 <- inner_join(Sullivan_dp05_2018, dp_table_variables, by = "variable")

Hawkins_dp02_18 <- inner_join(Hawkins_dp02_2018, dp_table_variables, by = "variable")

Hawkins_dp03_18 <- inner_join(Hawkins_dp03_2018, dp_table_variables, by = "variable")

Hawkins_dp04_18 <- inner_join(Hawkins_dp04_2018, dp_table_variables, by = "variable")

Hawkins_dp05_18 <- inner_join(Hawkins_dp05_2018, dp_table_variables, by = "variable")


Sullivan_data_profile <- rbind(Sullivan_dp02_18, Sullivan_dp03_18, Sullivan_dp04_18, Sullivan_dp05_18)

Hawkins_data_profile <- rbind(Hawkins_dp02_18, Hawkins_dp03_18, Hawkins_dp04_18, Hawkins_dp05_18)

combined_tract_dp <- rbind(Sullivan_data_profile, Hawkins_data_profile)

Sullivan_County_dp02_2018 <- get_acs(geography = "county", county = "Sullivan", state = "TN", table = "DP02", year = 2018, geometry = TRUE)

Sullivan_County_dp03_2018 <- get_acs(geography = "county", county = "Sullivan", state = "TN", table = "DP03", year = 2018, geometry = TRUE)

Sullivan_County_dp04_2018 <- get_acs(geography = "county", county = "Sullivan", state = "TN", table = "DP04", year = 2018, geometry = TRUE)

Sullivan_County_dp05_2018 <- get_acs(geography = "county", county = "Sullivan", state = "TN", table = "DP05", year = 2018, geometry = TRUE)

Hawkins_County_dp02_2018 <- get_acs(geography = "county", county = "Hawkins", state = "TN", table = "DP02", year = 2018, geometry = TRUE)

Hawkins_County_dp03_2018 <- get_acs(geography = "county", county = "Hawkins", state = "TN", table = "DP03", year = 2018, geometry = TRUE)

Hawkins_County_dp04_2018 <- get_acs(geography = "county", county = "Hawkins", state = "TN", table = "DP04", year = 2018, geometry = TRUE)

Hawkins_County_dp05_2018 <- get_acs(geography = "county", county = "Hawkins", state = "TN", table = "DP05", year = 2018, geometry = TRUE)

Sullivan_County_dp02_18 <- inner_join(Sullivan_County_dp02_2018, dp_table_variables, by = "variable")

Sullivan_County_dp03_18 <- inner_join(Sullivan_County_dp03_2018, dp_table_variables, by = "variable")

Sullivan_County_dp04_18 <- inner_join(Sullivan_County_dp04_2018, dp_table_variables, by = "variable")

Sullivan_County_dp05_18 <- inner_join(Sullivan_County_dp05_2018, dp_table_variables, by = "variable")

Hawkins_County_dp02_18 <- inner_join(Hawkins_County_dp02_2018, dp_table_variables, by = "variable")

Hawkins_County_dp03_18 <- inner_join(Hawkins_County_dp03_2018, dp_table_variables, by = "variable")

Hawkins_County_dp04_18 <- inner_join(Hawkins_County_dp04_2018, dp_table_variables, by = "variable")

Hawkins_County_dp05_18 <- inner_join(Hawkins_County_dp05_2018, dp_table_variables, by = "variable")


Sullivan_County_data_profile <- rbind(Sullivan_County_dp02_18, Sullivan_County_dp03_18, Sullivan_County_dp04_18, Sullivan_County_dp05_18)

Hawkins_County_data_profile <- rbind(Hawkins_County_dp02_18, Hawkins_County_dp03_18, Hawkins_County_dp04_18, Hawkins_County_dp05_18)

combined_county_dp <- rbind(Sullivan_County_data_profile, Hawkins_County_data_profile)

```
## Age

Sullivan County had an estimated total population of 156,734 individuals, with the median age being 44.9 years. 80.4% of the population is above 18 years of age.  

```{r Age Data Table, echo = FALSE}




```

```{r median age census tract map, echo = FALSE}
median_age_tract <- combined_tract_dp %>%
  filter(variable == "DP05_0018") 
  

median_age_county <- combined_county_dp %>%
  filter(variable == "DP05_0018")

median_age_tract_map <- mapview(median_age_tract, zcol = "estimate", layer.name = "Median Age for Census Tracts")


###the county overview doesn't really need a legend
median_age_county_map <- mapview(median_age_county, zcol = "estimate", layer.name = "Median Age County", legend = FALSE)

median_age_map <-  median_age_county_map + median_age_tract_map

median_age_map


```



```{r data table test for tracts, echo = FALSE}

age_vars <- c("DP05_0001",  "DP05_0005",  "DP05_0006",  "DP05_0007",  "DP05_0008",  "DP05_0009",
               "DP05_0010",  "DP05_0011",  "DP05_0012",  "DP05_0013",  "DP05_0014", 
              "DP05_0015",  "DP05_0016",  "DP05_0017",  "DP05_0018",  "DP05_0021",  "DP05_0024"
              )

age_vars_percent <- c("DP05_0001P", "DP05_0005P",  "DP05_0006P", "DP05_0007P",  "DP05_0008P", 
              "DP05_0009P",  "DP05_0010P",  "DP05_0011P", "DP05_0012P",  "DP05_0013P",  "DP05_0014P",
               "DP05_0015P", "DP05_0016P",  "DP05_0017P",  "DP05_0018P",  "DP05_0021P", 
              "DP05_0024P")

sull_col_dt_names_reg <- c("Total Population",  
                      "Age Under 5 Years", "Age 5-9 Years", "Age 10-14 Years",  "Age 15-19 Years", 
                       "Age 20-24 Years",  "Age 25-34 Years",  "Age 35-44 Years",  
                       "Age 45-54 Years",  "Age 55-59 Years",  "Age 60-64 Years", 
                       "Age 65-74 Years",  "Age 75-84 Years",  "Age 85+ Years",  
                       "Median Age", "Age 18+ Years",  "Age 65+ Years")

sull_col_dt_names_percent <- c("Total Population Percentage","Age Under 5 Years Percentage","Age 5-9 Years Percentage", "Age 10-14 Years Percentage","Age 15-19 Years Percentage", "Age 20-24 Years Percentage",
                               "Age 25-34 Years Percentage", "Age 35-44 Years Percentage", "Age 45-54 Years Percentage", "Age 55-59 Years Percentage", "Age 60-64 Years Percentage", "Age 65-74 Years Percentage",
                               "Age 75-84 Years Percentage","Age 85+ Years Percentage","Median Age Percentage", "Age 18+ Years Percentage", "Age 65+ Years Percentage" )



dt_age_tract_counts <- combined_tract_dp %>%
  filter(variable %in% age_vars)

dt_age_county_counts <- combined_county_dp %>%
  filter(variable %in% age_vars)

dt_age_tract_percent <- combined_tract_dp %>%
  filter(variable %in% age_vars_percent)

dt_age_county_percent <- combined_county_dp %>%
  filter(variable %in% age_vars_percent)



age_tract_df <- cbind(sull_col_dt_names_reg, dt_age_tract_counts, dt_age_tract_percent)

age_tract_dt <- age_tract_df[,c(1,3,5,6,12,13)]

age_dt <- st_set_geometry(age_tract_dt, NULL)

age_dt_names <- c("Age Group", "Census Tract", "Count Estimate", "Count Margin of Error", "Percent of Total Population", "Percent Margin of Error")

names(age_dt) <- age_dt_names

age_data_table <- datatable(age_dt)


```

```{r data table for counties, echo = FALSE}

age_vars <- c("DP05_0001",  "DP05_0005",  "DP05_0006",  "DP05_0007",  "DP05_0008",  "DP05_0009",
               "DP05_0010",  "DP05_0011",  "DP05_0012",  "DP05_0013",  "DP05_0014", 
              "DP05_0015",  "DP05_0016",  "DP05_0017",  "DP05_0018",  "DP05_0021",  "DP05_0024"
              )

age_vars_percent <- c("DP05_0001P", "DP05_0005P",  "DP05_0006P", "DP05_0007P",  "DP05_0008P", 
              "DP05_0009P",  "DP05_0010P",  "DP05_0011P", "DP05_0012P",  "DP05_0013P",  "DP05_0014P",
               "DP05_0015P", "DP05_0016P",  "DP05_0017P",  "DP05_0018P",  "DP05_0021P", 
              "DP05_0024P")

sull_col_dt_names_reg <- c("Total Population",  
                      "Age Under 5 Years", "Age 5-9 Years", "Age 10-14 Years",  "Age 15-19 Years", 
                       "Age 20-24 Years",  "Age 25-34 Years",  "Age 35-44 Years",  
                       "Age 45-54 Years",  "Age 55-59 Years",  "Age 60-64 Years", 
                       "Age 65-74 Years",  "Age 75-84 Years",  "Age 85+ Years",  
                       "Median Age", "Age 18+ Years",  "Age 65+ Years")

sull_col_dt_names_percent <- c("Total Population Percentage","Age Under 5 Years Percentage","Age 5-9 Years Percentage", "Age 10-14 Years Percentage","Age 15-19 Years Percentage", "Age 20-24 Years Percentage",
                               "Age 25-34 Years Percentage", "Age 35-44 Years Percentage", "Age 45-54 Years Percentage", "Age 55-59 Years Percentage", "Age 60-64 Years Percentage", "Age 65-74 Years Percentage",
                               "Age 75-84 Years Percentage","Age 85+ Years Percentage","Median Age Percentage", "Age 18+ Years Percentage", "Age 65+ Years Percentage" )


###need to make the tables for the counties, and like top 10 or something for the tracts###

dt_age_county_counts <- combined_county_dp %>%
  filter(variable %in% age_vars)

dt_age_county_percent <- combined_county_dp %>%
  filter(variable %in% age_vars_percent)

age_county_df <- cbind(sull_col_dt_names_reg, dt_age_county_counts, dt_age_county_percent)

age_county_dt <- age_county_df[,c(1,3,5,6,12,13)]

age_county_dt <- st_set_geometry(age_county_dt, NULL)

age_dt_county_names <- c("Age Group", "County", "Count Estimate", "Count Margin of Error", "Percent of Total Population", "Percent Margin of Error")

names(age_county_dt) <- age_dt_county_names

age_county_data_table <- datatable(age_county_dt, caption = "Table 1: Sullivan and Hawkins County, Tennessee Age Groups")

age_county_data_table



```

```{r Disability data tables, echo = FALSE}
#### Disability status ####  
    
    disability_vars_18 <- c("DP02_0070", "DP02_0071", "DP02_0072", "DP02_0073", "DP02_0074", "DP02_0075", "DP02_0076", "DP02_0077")
    
    disability_percent_vars_18 <- c("DP02_0070P", "DP02_0071P", "DP02_0072P", "DP02_0073P", "DP02_0074P", "DP02_0075P", "DP02_0076P", "DP02_0077P")
    
    disability_vars_names_18 <- c("Total Civilian Population", "Civilian Population with a Disability","Total Civilian Population Under 18 Years of Age", "Civilian Population Under 18 Years of Age with a Disability",
                                  "Total Civilain Population Ages 18-64", "Civilian Population Ages 18-74 with a Disability", "Total Civilian Population Over 65 Years of Age", "Civilian Population Over 65 Years of Age with a Disability")
    
    
    
    df_disability_tract_counts_18 <- combined_tract_dp_18 %>%
      filter(variable %in% disability_vars_18)
    
    df_disability_county_counts_18 <- combined_county_dp_18 %>%
      filter(variable %in% disability_vars_18)
    
    df_disability_tract_percent_18 <- combined_tract_dp_18 %>%
      filter(variable %in% disability_percent_vars_18)
    
    df_disability_county_percent_18 <- combined_county_dp_18 %>%
      filter(variable %in% disability_percent_vars_18)
    
    df_disability_kpt_counts_18 <- kpt_data_profile_18 %>%
      filter(variable %in% disability_vars_18)
    
    df_disability_kpt_percent_18 <- kpt_data_profile_18 %>%
      filter(variable %in% disability_percent_vars_18)
    
    
    ##combine the percents into one table
    
    df_disability_tract_18 <- cbind(disability_vars_names_18, df_disability_tract_counts_18, df_disability_tract_percent_18)
    
    df_disability_county_18 <- cbind(disability_vars_names_18, df_disability_county_counts_18, df_disability_county_percent_18)
    
    df_disability_kpt_18 <- cbind(disability_vars_names_18, df_disability_kpt_counts_18, df_disability_kpt_percent_18)
    
    
    disable_names <- names(df_disability_county_18)
    
    disable_names_2 <- disable_names[-c(16,17)]
    
    names(df_disability_kpt_18) <- disable_names_2
    
    disability_kpt_18_for_map <- left_join(kpt_18, df_disability_kpt_18, by = "GEOID") #this has the location data
    
    
    
    trimmed_df_disability_tract_18 <- df_disability_tract_18[,c(1,3,5,6,12,13)] #these are the ones with the location data
    
    trimmed_df_disability_county_18 <- df_disability_county_18[,c(1,3,5,6,12,13)] #these are the ones with the location data
    
    trimmed_df_disability_kpt_18 <- df_disability_kpt_18[,c(1,5,6,12,13)] # no location data
    
    
    ##get ride of location data for the tract/county
    
    data_table_disability_tract_18 <- st_set_geometry(trimmed_df_disability_tract_18, NULL)
    
    data_table_disability_county_18 <- st_set_geometry(trimmed_df_disability_county_18, NULL)
    
    data_table_disability_kpt_18 <- trimmed_df_disability_kpt_18
    
    ##rename the columns 
    
    
    disability_table_tract_names <- c("Disability Measure", "Census Tract", "Count", "Margin of Error", "Percent", "Percent Margin of Error")
    
    disability_table_county_names <- c("Disability Measure", "County", "Count", "Margin of Error", "Percent", "Percent Margin of Error")  
    
    disability_table_kpt_names <- c("Disability Measure", "Count", "Margin of Error", "Percent", "Percent Margin of Error")
    
    names(data_table_disability_tract_18) <- disability_table_tract_names
    
    names(data_table_disability_county_18) <- disability_table_county_names
    
    names(data_table_disability_kpt_18) <- disability_table_kpt_names
    
    ##make the data tables
    
    disability_tract_data_table_18 <- datatable(data_table_disability_tract_18, caption = "Disability Characteristics of Census Tract Groups for Sullivan and Hawkins County, Tennessee 2018")
    
    disability_county_data_table_18 <- datatable(data_table_disability_county_18, caption = "Disability Characteristics for Sullivan and Hawkins County, Tennessee 2018")
    
    disability_kpt_data_table_18 <- datatable(data_table_disability_kpt_18, caption = "Disability Characteristics for Kingsport, Tennessee 2018")
    
    disability_tract_data_table_18
    
    disability_county_data_table_18
    
    disability_kpt_data_table_18

```

```{r Percent Disability Map, echo = FALSE}
##percent disability or greater map
    
    disability_tract_map_names <- c("Disability Measure", "Census Tract", "Count", "Count MOE", "Percent", "Percent MOE", "geometry")
    
    disability_county_map_names <- c("Disability Measure", "County", "Count", "Count MOE", "Percent", "Percent MOE", "geometry")
    
    trimmed_disability_kpt_18_for_map <- disability_kpt_18_for_map[,c(15,16,18,19,25,26)]
    
    disability_kpt_map_names <- c("Disability Measure", "Kingsport", "Count", "Count MOE", "Percent", "Percent MOE", "geometry")
    
    names(trimmed_df_disability_county_18) <- disability_county_map_names
    
    names(trimmed_df_disability_tract_18) <- disability_tract_map_names
    
    names(trimmed_disability_kpt_18_for_map) <- disability_kpt_map_names
    
    percent_disabled_county <- trimmed_df_disability_county_18 %>%
      filter(`Disability Measure` == "Civilian Population with a Disability")
    
    
    percent_disabled_tract <- trimmed_df_disability_tract_18 %>%
      filter(`Disability Measure` == "Civilian Population with a Disability")
    
    percent_disabled_kpt <- trimmed_disability_kpt_18_for_map %>%
      filter(`Disability Measure` == "Civilian Population with a Disability")
    
    disability_map <- mapview(list(percent_disabled_county, percent_disabled_tract, percent_disabled_kpt),
                                zcol = list("Percent", "Percent", NULL),
                                layer.name = list("Percent Population with a Disability County", "Percent Population with a Disability Tract", "Percent Population with a Disability City"),
                                legend = list(FALSE, TRUE, FALSE))
    disability_map
    


```
```{r residence 1 year ago, echo = FALSE}

    residence_vars_18 <- c("DP02_0079", "DP02_0080", "DP02_0081", "DP02_0082", "DP02_0083", "DP02_0084", "DP02_0085")
    
    residence_percent_vars_18 <- c("DP02_0079P", "DP02_0080P", "DP02_0081P", "DP02_0082P", "DP02_0083P", "DP02_0084P", "DP02_0085P")
    
    residence_vars_names_18 <- c("Residence 1 Year Ago in same House", "Residence 1 Year Ago in Different House in US", "Residence 1 Year Ago in Different House in Same County",
                                 "Residence 1 Year Ago in Different House Different County", "Residence 1 Year Ago in Different House Same State", "Residence 1 Year Ago in Different House Different State",
                                 "Residence 1 Year Ago in Different House Abroad")
    
    
    df_residence_tract_counts_18 <- combined_tract_dp_18 %>%
      filter(variable %in% residence_vars_18)
    
    df_residence_county_counts_18 <- combined_county_dp_18 %>%
      filter(variable %in% residence_vars_18)
    
    df_residence_tract_percent_18 <- combined_tract_dp_18 %>%
      filter(variable %in% residence_percent_vars_18)
    
    df_residence_county_percent_18 <- combined_county_dp_18 %>%
      filter(variable %in% residence_percent_vars_18)
    
    df_residence_kpt_counts_18 <- kpt_data_profile_18 %>%
      filter(variable %in% residence_vars_18)
    
    df_residence_kpt_percent_18 <- kpt_data_profile_18 %>%
      filter(variable %in% residence_percent_vars_18)
    
    
    ##combine the percents into one table
    
    df_residence_tract_18 <- cbind(residence_vars_names_18, df_residence_tract_counts_18, df_residence_tract_percent_18)
    
    df_residence_county_18 <- cbind(residence_vars_names_18, df_residence_county_counts_18, df_residence_county_percent_18)
    
    df_residence_kpt_18 <- cbind(residence_vars_names_18, df_residence_kpt_counts_18, df_residence_kpt_percent_18)
    
    
    res_names <- names(df_residence_county_18)
    
    res_names_2 <- res_names[-c(16,17)]
    
    names(df_residence_kpt_18) <- res_names_2
    
    residence_kpt_18_for_map <- left_join(kpt_18, df_residence_kpt_18, by = "GEOID") #this has the location data
    
    
    
    trimmed_df_residence_tract_18 <- df_residence_tract_18[,c(1,3,5,6,12,13)] #these are the ones with the location data
    
    trimmed_df_residence_county_18 <- df_residence_county_18[,c(1,3,5,6,12,13)] #these are the ones with the location data
    
    trimmed_df_residence_kpt_18 <- df_residence_kpt_18[,c(1,5,6,12,13)] # no location data
    
    
    ##get ride of location data for the tract/county
    
    data_table_residence_tract_18 <- st_set_geometry(trimmed_df_residence_tract_18, NULL)
    
    data_table_residence_county_18 <- st_set_geometry(trimmed_df_residence_county_18, NULL)
    
    data_table_residence_kpt_18 <- trimmed_df_residence_kpt_18
    
    ##rename the columns 
    
    
    residence_table_tract_names <- c("Residence Measure", "Census Tract", "Count", "Margin of Error", "Percent", "Percent Margin of Error")
    
    residence_table_county_names <- c("Residence Measure", "County", "Count", "Margin of Error", "Percent", "Percent Margin of Error")  
    
    residence_table_kpt_names <- c("Residence Measure", "Count", "Margin of Error", "Percent", "Percent Margin of Error")
    
    names(data_table_residence_tract_18) <- residence_table_tract_names
    
    names(data_table_residence_county_18) <- residence_table_county_names
    
    names(data_table_residence_kpt_18) <- residence_table_kpt_names
    
    ##make the data tables
    
    residence_tract_data_table_18 <- datatable(data_table_residence_tract_18, caption = "Residence Characteristics of Census Tract Groups for Sullivan and Hawkins County, Tennessee 2018")
    
    residence_county_data_table_18 <- datatable(data_table_residence_county_18, caption = "Residence Characteristics for Sullivan and Hawkins County, Tennessee 2018")
    
    residence_kpt_data_table_18 <- datatable(data_table_residence_kpt_18, caption = "Residence Characteristics for Kingsport, Tennessee 2018")
    
    residence_tract_data_table_18
    
    residence_county_data_table_18
    
    residence_kpt_data_table_18
```

```{r different state map, echo = FALSE}
#residence less than 1 year percent out of state map
    
    residence_tract_map_names <- c("Residence Measure", "Census Tract", "Count", "Count MOE", "Percent", "Percent MOE", "geometry")
    
    residence_county_map_names <- c("Residence Measure", "County", "Count", "Count MOE", "Percent", "Percent MOE", "geometry")
    
    trimmed_residence_kpt_18_for_map <- residence_kpt_18_for_map[,c(15,16,18,19,25,26)]
    
    residence_kpt_map_names <- c("Residence Measure", "Kingsport", "Count", "Count MOE", "Percent", "Percent MOE", "geometry")
    
    names(trimmed_df_residence_county_18) <- residence_county_map_names
    
    names(trimmed_df_residence_tract_18) <- residence_tract_map_names
    
    names(trimmed_residence_kpt_18_for_map) <- residence_kpt_map_names
    
    
    
    percent_residence_diff_state_county <- trimmed_df_residence_county_18 %>%
      filter(`Residence Measure` == "Residence 1 Year Ago in Different House Different State")
    
    
    percent_residence_diff_state_tract <- trimmed_df_residence_tract_18 %>%
      filter(`Residence Measure` == "Residence 1 Year Ago in Different House Different State")
    
    percent_residence_diff_state_kpt <- trimmed_residence_kpt_18_for_map %>%
      filter(`Residence Measure` == "Residence 1 Year Ago in Different House Different State")
    
    residence_diff_state_map <- mapview(list(percent_residence_diff_state_county, percent_residence_diff_state_tract, percent_residence_diff_state_kpt),
                                        zcol = list("Percent", "Percent", NULL),
                                        layer.name = list("Percent Residence in a Different State 1 Year Ago County", "Percent Residence in a Different State 1 Year Ago Tract", "Percent Residence in a Different State 1 Year Ago City"),
                                        legend = list(FALSE, TRUE, FALSE))
    
    residence_diff_state_map

```

## References 

---
nocite: '@*'
...
